Questions to Developers

### 2021-06-25 StateOfPractice/Ao-Notes/DomainExptMeeting/Presentation for the Introductory Meeting.tex
updated software lists

\begin{multicols}{2}	
  \bi
\item 
\ei
\end{multicols}

@@

%\begin{multicols}{2}	
  \bi
\item 
	\ei
%\end{multicols}

@@

\begin{multicols}{2}	
  \bi
			\item 
	\ei
\end{multicols}

>>>>

\bi
\item 3DSlicer
\item Horos
\item ImageJ
\item Fiji (a ``batteries-included" distribution of ImageJ)
\item Mango (on the initial list, but not the final list)
\item Papaya (the web version of Mango)
\item MRIcroGL (MRIcron development has moved to MRIcroGL)
\ei

@@

\bi
\item AFNI \hyperlink{https://afni.nimh.nih.gov}{https://afni.nimh.nih.gov}
\item FSL \hyperlink{https://fsl.fmrib.ox.ac.uk/fsl/fslwiki}{https://fsl.fmrib.ox.ac.uk/fsl/fslwiki} 
\item Freesurfer \hyperlink{https://surfer.nmr.mgh.harvard.edu}{https://surfer.nmr.mgh.harvard.edu} 
\item Tarquin \hyperlink{http://tarquin.sourceforge.net}{http://tarquin.sourceforge.net}  (for MRSpectroscopy data)
\item Diffusion Toolkit  \hyperlink{http://trackvis.org/dtk/}{http://trackvis.org/dtk/} (diffusion toolkit and trakVis)
\item MRItrix \hyperlink{https://www.mrtrix.org}{https://www.mrtrix.org}
\ei

@@

\begin{multicols}{2}	
\bi
\item Ginkgo CADx
\item XMedCon
\item Weasis
\item SMILI
\item DicomBrowser
\item 3DimViewer
\item OsiriX Lite
\item dwv
\item Drishti
\item BioImage Suite Web
\item OHIF Viewer
\item Slice:Drop
\item GATE
\item ITK-SNAP
\item ParaView
\item MatrixUser
\item DICOM Viewer
\item INVESALIUS 3
\item medInria
\item dicompyler
\item MicroView
\item AMIDE
\item Gwyddion
\ei
\end{multicols}
